Proposal to improve BBC Search through the use of Linked Data

### 2014-05-20 chapter1.tex
Done! Reviewed and ready to submit.

\begin{enumerate}
  \item Further decoupling of BBC applications, which aids scalability,
    maintainability and resilience in many software architectures.
  \item Improvements to the search results page that help users determine
    if the results given are relevant. The example of this is by using
    \emph{Rich Snippets}\cite{goel2009introducing}
    that can automatically display some semantic information about a given
    result without the need for manual curation.
  \item User experience and design improvements to the search results
    where semantic properties about the results can drive visual decoration
    and calls to action.
  \item Removal of the exclusively manual curation of the ``Editor's Choice'' results
    against a given query and replacing it with curated linked data that
    can provide recommended content against queries in a more general
    manner.
\end{enumerate}

In the rest of this chapter, I will give an overview of what role BBC
Search plays and the distinct subsystems that it comprises.
In later chapters we can then look to improve these systems
how these improvements might complement each other.

@@

\begin{displaymath}
  \textbf{recall} = \frac{
    |{relevant documents} \cap \text{retrieved documents}|
  }{
    |\text{relevant documents}|
  }
\end{displaymath}

>>>>

\begin{enumerate}
  \item Further decoupling of BBC applications, which aids scalability,
    maintainability and resilience in many software architectures.
  \item Improvements to the search results page that help users determine
    if the results given are relevant. The example of this is by using
    \emph{Rich Snippets}\cite{goel2009introducing}
    that can automatically display some semantic information about a given
    result without the need for manual curation.
  \item User experience and design improvements to the search results
    where semantic properties about the results can drive visual decoration
    and calls to action.
  \item More automation of the curation of the ``Editor's Choice'' results
    against a given query and replacing it with curated linked data that
    can provide recommended content against queries in a more general
    manner.
\end{enumerate}

In the rest of this chapter, I will give an overview of what r\^ole BBC
Search plays and the distinct subsystems that it comprises.
In later chapters we can then look to improve these systems
how these improvements might complement each other.

@@

\begin{displaymath}
  \textbf{recall} = \frac{
    |\text{relevant documents} \cap \text{retrieved documents}|
  }{
    |\text{relevant documents}|
  }
\end{displaymath}

### 2014-05-20 chapter2.tex
Done! Reviewed and ready to submit.

\begin{enumerate}
\item Use URIs to denote things, whether pages/documents on the web
  or real physical and conceptual things in the world.
\item Prefer HTTP URIs (i.e. URLs) so that they can be looked
  up (i.e. \emph{dereferenced} to get more information about the thing denoted.
\item When these URIs are dereferenced, provide useful information about
  those things using web standards, e.g. RDF, HTML, XML, Turtle.
\item Include links to other things (using their URIs) when such
  information is published on the web.
\end{enumerate}

This overlaps somewhat Semantic Web techniques and it builds upon
the \emph{Resource Description Framework} (RDF)\cite{lassila1999resource},
which is a general-purpose method for describing and modelling information.

@@

Using one or more of these approaches allows a publisher to convey
machine-readable metadata in the same document that is served to humans.
This allows, for example, search engines to index more categorical and
structured information about a page when it is crawled in addition to the
normal processing on the text content. This was the foundation of the
Semantic Web\cite{berners2001semantic} before the term Linked Data
emerged and the aspiration was that widespread adoption would lead to
a comprehensive ``Web of Data'' to rival the rich, so-called
``Web of Documents'' that is the World Wide Web as we know it as a collection
of human-readable pages.

@@

All of the above approaches can be found ``in the wild'' in pages across
the Web with differing rates of adoption.\cite{haas2011enhanced}
General-purpose web search
engines can make use of this additional metadata to improve the quality
of the search results in a number of ways. In section~\ref{enhancing-results},
I discuss some of these potential improvements.

@@

Evaluation of the effectiveness of search results enhanced with rich snippets
via both explicit and implicit user feedback had been carried out by
Haas et al.\cite{haas2011enhanced} at Microsoft and Yahoo! research. The
results showed a promising preference from 84\% of users for a result
with enhanced information with the most common downside being that the
snippet may sometimes present incorrect information (e.g. showing the wrong
price for a product is less preferable than simply not attempting to present
the price at all). Implicit feedback via click-through rates (CTR) --
a common metric to indicate that users are happy enough with the information
given to click on the link given -- suggested users were more likely to
follow enhanced results.

@@

\emph{Enterprise integration} is an important technical field within the
discipline of Enterprise Architecture that focuses on interconnecting
systems and allowing data to flow between them. This can be seen as
the practice of breaking down information silos that naturally emerge
in enterprise organisations.\cite{allemang2010semantic}

@@

There are difficulties with some of these approaches noted by
Allemang\cite{allemang2010semantic}. Data warehousing,
integration projects and metadata repositories can all
be time-consuming to implement, require repeated updating when
use cases change and at the extreme can be seen as solving the
problem of too many silos by adding another silo.

@@

If we view the indexing processes
of a search application as a variant of data warehousing,
we can start to argue for enterprise-wide publishing of
linked data as a more cost effective means of building search

>>>>

\begin{enumerate}
\item Use URIs to denote things, whether pages/documents on the web
  or real, physical and conceptual things in the world.
\item Prefer HTTP URIs (i.e. URLs) so that they can be looked
  up (i.e. \emph{dereferenced}) to get more information about the thing denoted.
\item When these URIs are dereferenced, provide useful information about
  those things using web standards, e.g. RDF, HTML, XML, Turtle.
\item Include links to other things (using their URIs) when such
  information is published on the web.
\end{enumerate}

This overlaps somewhat with Semantic Web techniques and it builds upon
the \emph{Resource Description Framework} (RDF)\cite{lassila1999resource},
which is a general-purpose method for describing and modelling information.

@@

Using one or more of these approaches allows a publisher to convey
machine-readable metadata in the same document that is served to humans.
This allows, for example, search engines to index more categorical and
structured information about a page when it is crawled in addition to the
normal processing on the text content. This was the foundation of the
Semantic Web\cite{berners2001semantic} before the term Linked Data
emerged and the aspiration was that widespread adoption would lead to
a comprehensive ``Web of Data'' to rival the rich, so-called
``Web of Documents'' that is the World Wide Web as we know it -- a collection
of human-readable pages.

@@

All of the above approaches can be found ``in the wild'' in pages across
the Web with differing rates of adoption.\cite{haas2011enhanced}
General-purpose web search
engines can make use of this additional metadata to improve the quality
of the search results in a number of ways. In section~\ref{enhancing-results},
some of these potential improvements are discussed.

@@

Evaluation of the effectiveness of search results enhanced with rich snippets
via both explicit and implicit user feedback had been carried out by
Haas et al.\cite{haas2011enhanced} at Microsoft and Yahoo! research. The
results showed a promising preference from 84\% of users for a result
with enhanced information with the most common downside being that the
snippet may sometimes present incorrect information (e.g. showing the wrong
price for a product is less preferable to simply not attempting to present
the price at all). Implicit feedback via click-through rates (CTR) --
a common metric to indicate that users are happy enough with the information
given to click on the link given -- suggested users were more likely to
follow enhanced results.

@@

\emph{Enterprise Integration} is an important technical field within the
discipline of \emph{Enterprise Architecture} that focuses on interconnecting
systems and allowing data to flow between them. This can be seen as
the practice of breaking down information silos that naturally emerge
in enterprise organisations.\cite{allemang2010semantic}

@@

However, There are difficulties with some of these approaches -- as noted by
Allemang\cite{allemang2010semantic}. Data warehousing,
integration projects and metadata repositories can all
be time-consuming to implement, require repeated updating when
use cases change and at the extreme can be seen as solving the
problem of too many silos by adding another silo.

@@

If we view the indexing processes
of a search application as a variant of data warehousing,
we can start to argue for enterprise-wide publishing of
linked data as a more cost effective means of building search
indexes that bring together all published content.

### 2014-05-20 chapter3.1.tex
Did some reviewing and trrying to fit diagrams in.
Done! Reviewed and ready to submit.

We can achieve some uniformity of the data by building a single, common
API through which all content is fed into the Search application. However,
some integration work needs to be
done by either the owners of the content to send content to the API
or the developers of the Search application, who can integrate
existing feeds via an adapter pattern.

@@

\begin{sidewaysfigure}
  \begin{center}
\begin{dot2tex}[dot,scale=0.6]
digraph ingest {
  rankdir=TB;

  Programmes [shape=rect]
  News [shape=rect]
  Newsround [shape=rect]
  Newsbeat [shape=rect]
  Sport [shape=rect]
  MarketData [shape=rect]
  WorldService [shape=rect]
  BBCFood [shape=rect]
  ProgrammesWebsites [shape=rect]
  LegacyWebsites [shape=rect]

  SearchIndexes [shape=circle]

@@

  ProgrammesWebsites -> Crawler
  BBCFood -> Crawler
  LegacyWebsites -> Crawler
  trans2 [label="Transformation"]
  Crawler -> trans2
  trans2 -> IngestAPI

@@

It is clear that the search application has the need to normalise vocabularies
to some extent (e.g. is it ``title'', ``headline'' or ``display title''
that I should display as the link text on the results page?) and this requires
some form of transformation. This frames the search application as being a
key system whose primary r\^ole is to break down all the content silos in the
BBC, which was noted as a motivation for Linked Data in chapter 2.

There is also an apparent requirement that we are cautious of delegating
too much integration work to other teams. From the perspective of teams
whose products produce content, the ideal search system would be
``light touch'' and reasonably passive at indexing their content. This
expectation is strengthened by the long history of public, general-purpose
web search engines such as Google who seem to find websites by themselves
and index them without any input from webmasters. However, it should
not be overlooked that Google does in fact place some burden on webmasters
to increase the crawlability and indexability of their websites. This
burden is welcomed due to the benefits of higher rankings that emerge
after sinking those costs.

@@

\subsection{The Content}
\label{content}

The front end search application currently divides all the searchable
content into so-called ``zones''. Table~\ref{zones-table}

%TODO - is this all of them?
\begin{sidewaysfigure}
  \centering
\begin{tabular}{| p{5cm} | p{16cm} |}
  \hline
  Zone/Category          & Notes/Comments \\
  \hline
  About the BBC          &  Static pages, blogs, articles. RSS/Atom feeds available. \\
  \hline
  Blogs                  &  Legacy blog content. RSS/Atom available. \\
  \hline
  CBBC                   &  Pages, games, programmes information for Children. Some semantic markup exists for Facebook's Open Graph. \\
  \hline
  Films                  &  Legacy site for BBC Film Network and current site for BBC Films. Little semantic markup. \\
  \hline
  Food                   &  Recipes features on BBC programmes. No semantic markup despite sister website BBC Good Food website using Schema.org microdata. \\
  \hline
  Gardening              &  Legacy website not updated since 2006. All static HTML content with no semantic markup. \\
  \hline
  Health \& Parenting    &  \\
  \hline
  History                &  \\
  \hline
  iPlayer                &  \\
  \hline
  Learning               &  \\
  \hline
  Local (archive)        &  \\
  \hline
  Music                  &  \\
  \hline
  News                   &  \\
  \hline
  Ouch!                  &  \\
  \hline
  Religion \& Ethics     &  \\
  \hline
  Science \& Nature      &  \\
  \hline
  Sport                  &  \\
  \hline
  Teenagers              &  \\
  \hline
  TV \& Radio Programmes &  \\
  \hline
  TV \& Radio Sites      &  \\
  \hline
\end{tabular}
\caption{Categories or ``zones'' of content currently indexed by BBC Search.}
\label{zones-table}
\end{sidewaysfigure}

@@

There is a wealth of legacy content that is likely to be obtainable only by
crawling. Some active sites are syndicated via RSS/Atom, but a subscription-based
feed does not allow indexing a backfill of content easily.

@@

In this case, this graph of metadata has come not just from microdata
in the home page, but also by merging it with the alternative RDF/XML
representation that appears to contain more detailed information.
It was necessary to have some knowledge of this behaviour of the
programmes microsites -- that they have multiple representations
in different media types -- since the microdata in the HTML view
does not link to the RDF/XML view in any way. Such small bits of
knowledge and business rules about the BBC's own online content
is a way a BBC-specific search product can gather information publically-available
as linked data, but in a more considered way and have advantages over
public search engines such as Google and Bing.

\begin{sidewaysfigure}
  \begin{center}
    \begin{dot2tex}[dot,pgf,scale=0.25]
      \input{question-time.dot}
    \end{dot2tex}
  \end{center}
  \caption{Semantic metadata found within \emph{Question Time} home page}
  \label{question-time}
\end{sidewaysfigure}

@@

The Question Time brand has associated metadata that might
be useful for a search application to display or index. A title
suitable for displaying is given along with synopses of two
different lengths, which might form part of a snippet. We are also
told that the programme falls within \emph{genres} indentified
by \texttt{bbcprog:genres/factual/politics\#genre} and
\texttt{bbcprog:genres/news\#genre}. This URI pattern is
clear enough to a human reader to represent a \emph{Politics}
subgenre (underneath a \emph{Factual} genre) and a
\emph{News} genre respectively. However, if we wish to make
use of this in any applications, the correct approach with
linked data is to dereference those identifiers to find
metadata we can display or index.

Following the politics subgenre URL, we can produce the
semantic representation shown in figure~\ref{politics}.
An indexing process that follows certain linked entities
could, for example, index the Question Time home page
against the keywords ``politics'' or index a film's
page against the names of actors that appear therein.
Linked concepts might also drive decorations and controls
on the search results pages themselves or the search
application might even be able to provide faceting, filtering
and aggregation across content that shares common properties.

\begin{sidewaysfigure}
  \begin{center}
    \begin{dot2tex}[dot,pgf,scale=0.41]
      \input{politics.dot}
    \end{dot2tex}
  \end{center}
  \caption{Semantic metadata around the \emph{Politics} programme genre}
  \label{politics}
\end{sidewaysfigure}

@@

The time and date of the next broadcast of this episode is also shown.
From the graph depicted, we can see there is a (presumably repeat)
broadcast to occur on Sunday, 11 May 2014 on the BBC Parliament
channel. Again, this is information that can be displayed within
search results that might well answer some queries directly
such as ``When it Question Time next on TV?''. This is similar
to functionality offered by Google where currency conversions,
flight times and other quick answers are displayed at the top
of the results for any query it deems has a straight answer.

Finally, note there is some metadata about the pages themselves
that are repeated within the Open Graph protocol namespace
(prefixed with \texttt{og:}). It is common for BBC pages (and
in fact pages on the web in general) to have embedded Open
Graph metadata to integrate into Facebook's social graph, even
when no other semantic markup or metadata are present. Whilst
the original intention was for Facebook integration, linked
data technologies will allow us to derive information from
these properties beyond their intended purpose.

Overall, there are a lot of metadata obtainable about BBC
programmes via semantic markup available on the public web. There is
still some information that we cannot obtain:

\begin{itemize}
  \item We cannot easily gather a list of all identifiers that might
    be interesting to the search application. Crawling links is
    popular with web crawlers, but there is no guarantee of finding
    everything and there are difficulties knowing when to get an
    updated version of a page when it changes. A BBC-specific
    search can and arguably should make use of internal integration
    to discover and update programmes information as it is created,
    changed or removed.
  \item BBC iPlayer can display the names of contributors to a programme
    such as the producers, directors, actors, etc. This information
    does not appear to be present in the semantic metadata within
    the programmes microsites.
  \item Linked Data follows an \emph{Open World} assumption,
    which means that the lack of fact being asserted does not imply
    that fact is not true. In our Question Time example above, the
    fact that Question Time is not asserted to be a comedy does not
    strictly imply that it is not a comedy.
\end{itemize}

@@

In this example, missing off the link to iPlayer might merely
inconvenience a user who has to click around a bit more to
find the iPlayer link. If, however, the search application
chose not to respond with the programme at all under the
impression it is not available to watch, then there is an
arguably more broken user experience.

@@

The trade-offs between open and closed world assumptions need to
be kept in mind for any information architecture around the
search results pages and for any domain modelling for the
search indexes. Care should be taken around any design element
or feature that is affected the lack of information. Ideally,
all behaviour would follow a \emph{progressive enhancement} model
where additional information can only improve the system's
behaviour
and the omission of details or data leads to a \emph{degraded}
rather than \emph{broken} experience.

The programmes dataset is normally the most structured and
complex to work with, but is one of the leading uses of
semantic web technologies on the BBC website as a whole. In
the rest of this sectio, I will briefly touch on any different
challenges from other datasets.

@@

The semantic metadata that can be found in a BBC News article
page is notably less complex that a programmes microsite, as
can be seen in figure~\ref{keepod}.

\begin{sidewaysfigure}
  \begin{center}
    \begin{dot2tex}[dot,pgf,scale=0.41]
      \input{keepod.dot}
    \end{dot2tex}
  \end{center}
  \caption{Metadata found within a BBC News article page}
  \label{keepod}
\end{sidewaysfigure}

As discusseed in section~\ref{programmes}, BBC News also makes
use of Facebook's Open Graph metadata and a search application
could derive information about this article from those properties.

@@

\begin{sidewaysfigure}
  \begin{center}
    \begin{dot2tex}[dot,pgf,scale=0.41]
      \input{keepod-tagged.dot}
    \end{dot2tex}
  \end{center}
  \caption{BBC News article page's metadata enriched using DBPedia Spotlight}
  \label{keepod-tagged}
\end{sidewaysfigure}

@@

One remaining piece of information that is still lacking is
what News category in which the article falls. The BBC News
website has business rules around categorising all news
content -- e.g. \emph{Technology}, \emph{Scotland}, \emph{Education}
-- but this categorisation seems lacking from the semantic markup. The
current BBC Search application decorates all news results with
their respective news category, so an indexing chain using
the linked data within the news pages alone would need need
to enrich with that information.

@@

%TODO - Finish this

>>>>

Some uniformity of the data is achieved by a single, common
API through which all content is fed into the Search application. However,
some integration work needs to be
done by either the owners of the content to send content to the API
or the developers of the Search application, who can integrate
existing feeds via an adapter pattern.

@@

\begin{sidewaysfigure}
  \begin{center}
\begin{dot2tex}[dot,scale=0.7]
digraph ingest {
  rankdir=TB;

  subgraph cluster_0 {
    label = "BBC Websites";
    Programmes [shape=rect]
    News [shape=rect]
    Newsround [shape=rect]
    Newsbeat [shape=rect]
    Sport [shape=rect]
    MarketData [shape=rect,label="Market Data"]
    WorldService [shape=rect,label="World Service"]
    BBCFood [shape=rect,label="BBC Food"]
    ProgrammesWebsites [shape=rect,label="Programmes Microsites"]
    LegacyWebsites [shape=rect,label="Legacy Websites"]
  }

  subgraph cluster_1 {
    label = "Search Application";
    FileBasedQueues [label="Message Queues"]
    IngestAPI [label="Ingest API"]
    SearchIndexes [shape=circle]
    Crawler
    trans2 [label="Transformation"]
    Transformation
  }

  subgraph cluster_2 {
    Dynamite
    CPS
    label = "Back-end Services";
  }

@@

  ProgrammesWebsites -> Crawler
  BBCFood -> Crawler
  LegacyWebsites -> Crawler
  Crawler -> trans2
  trans2 -> IngestAPI

@@

It is clear that the search application has the need to normalise vocabularies
to some extent (e.g. is it ``title'', ``headline'' or ``display title''
that I should display as the link text on the results page?) and this requires
some form of transformation. This frames the search application as being a
key system whose primary r\^ole is to break down all the content silos in the
BBC. This aligns with the one of the major motivations of linked data, which
is to break down content silos within organisations or indeed globally.

It seems there needs to be consideration around balancing the amount of
integration work delegated to other teams. From the perspective of teams
whose products produce content, the ideal search system would be
``light touch'' and reasonably passive at indexing their content. This
expectation is strengthened by the long history of public, general-purpose
web search engines such as Google who seem to find websites by themselves
and index them without any input from webmasters. However, it should
not be overlooked that Google does in fact place some burden on webmasters
to increase the crawlability and indexability of their websites. This
burden is welcomed due to the benefits of higher rankings that emerge
after sinking those costs.

@@

\section{The Content}
\label{content}

The front end search application currently divides all the searchable
content into so-called ``zones''. Table~\ref{zones-table} explains
each of these categories.

\begin{sidewaystable}
  \centering
\begin{tabular}{| p{5cm} | p{16cm} |}
  \hline
  Zone/Category          & Notes/Comments \\
  \hline
  About the BBC          &  Static pages, blogs, articles. RSS/Atom feeds available. \\
  \hline
  Blogs                  &  Legacy blog content. RSS/Atom available. \\
  \hline
  CBBC                   &  Pages, games, programmes information for Children. Has semantic markup for Facebook's Open Graph. \\
  \hline
  Films                  &  Legacy site for BBC Film Network and current site for BBC Films. Little semantic markup. \\
  \hline
  Food                   &  Recipes features on BBC programmes. No semantic markup despite sister website BBC Good Food website using Schema.org microdata. \\
  \hline
  Gardening              &  Legacy website not updated since 2006. All static HTML content with no semantic markup. \\
  \hline
  Health \& Parenting    &  Websites about health, pregnancy, relationships, etc. Most have been left unchanged for several years and some have in fact been taken down, but entries still exist for the removed pages in the search indexes. \\
  \hline
  History                &  A mixture of legacy sites relating to history and a revamped History home page until the banner of the new ``Knowledge and Learning'' collection of sites. \\
  \hline
  iPlayer                &  On-demand catch-up service for TV and Radio programmes broadcast on the BBC. Videos are traditionally only available for 7 days (this will change to 30 days soon) after broadcast. \\
  \hline
  Learning               &  A vast collection of websites with learning materials for children and adults alike. The content varies from very old pages to maintained ones revamped under the ``Knowledge and Learning'' brand.\\
  \hline
  Local (archive)        &  Legacy pages aimed at different local areas of the UK. Newer content is generally under the remit of BBC News, which has sections for different UK regions and local news therein. \\
  \hline
  Music                  &  Sites about music artists, reviews of albums, BBC orchestras, etc. The artist pages are driven by semantic metadata (e.g. Musicbrainz, DBPedia), but only markup for Facebook's Open Graph occurs in the pages.\\
  \hline
  News                   &  News articles published over several years. The quality of the pages and the markup varies with the age of the content, but newer articles contain some semantic markup. \\
  \hline
  Ouch!                  &  Legacy posts for BBC's blog about disability. From April 2013, blogs became part of BBC News, but links to older posts remain in the indexes. \\
  \hline
  Religion \& Ethics     &  Website under the ``Knowledge and Learning'' giving information on religion, culture and traditions. \\
  \hline
  Science \& Nature      &  Old and new sites including the maintained Nature site, which uses semantic data to generate a lot of the content\cite{raimond2010use}, and the Science site -- another site under the ``Knowledge and Learning'' brand. \\
  \hline
  Sport                  &  Up-to-date articles and information about sport. BBC Sport some similarities with BBC News in terms of articles, but also has some more quantitative data such as match results and fixture dates. \\
  \hline
  Teenagers              &  Legacy ``Switch'' site aimed at teenagers covering music, TV and games. \\
  \hline
  TV \& Radio Programmes &  Programmes microsites for every programme, individual episodes and additional content such as clips and character information. This content is obtained currently by crawling. \\
  \hline
  TV \& Radio Sites      &  Crawled ``home'' pages for BBC TV and Radio services with crawled, legacy pages about BBC programmes before the common platform for programmes microsites was developed.\cite{raimond2010use} \\
  \hline
\end{tabular}
\caption{Categories or ``zones'' of content currently indexed by BBC Search.}
\label{zones-table}
\end{sidewaystable}

@@

There is a wealth of legacy content that is likely to be obtainable only by
crawling. Some active sites are syndicated via RSS/Atom, but a subscription-based
feed does not allow indexing a back-fill of content easily.

@@

In this case, this graph of metadata has come not just from microdata
in the home page, but also by merging it with the alternative RDF/XML
representation that appears to contain more detailed information.
It was necessary to have some knowledge of this behaviour of the
programmes microsites -- that they have multiple representations
in different media types -- since the microdata in the HTML view
does not link to the RDF/XML view in any way. Such small bits of
knowledge and business rules about the BBC's own online content
is a way a BBC-specific search product can gather information publicly-available
as linked data, but in a more considered way and have advantages over
public search engines such as Google and Bing.

\begin{sidewaysfigure}
  \begin{center}
    \begin{tikzpicture}[scale=0.35,transform shape]
    \begin{dot2tex}[dot,pgf,codeonly]
      \input{question-time.dot}
    \end{dot2tex}
    \end{tikzpicture}
  \end{center}
  \caption{Semantic metadata found within \emph{Question Time} home page}
  \label{question-time}
\end{sidewaysfigure}

@@

The Question Time brand has associated metadata that might
be useful for a search application to display or index. A title
suitable for displaying is given along with synopses of two
different lengths, which might form part of a snippet. We are also
told that the programme falls within \emph{genres} identified
by \texttt{bbcprog:genres/factual/politics\#genre} and
\texttt{bbcprog:genres/news\#genre}. This URI pattern is
clear enough to a human reader to represent a \emph{Politics}
sub-genre (underneath a \emph{Factual} genre) and a
\emph{News} genre respectively. However, if we wish to make
use of this in any applications, the correct approach with
linked data is to dereference those identifiers to find
metadata we can display or index.

Following the politics sub-genre URL, we can produce the
semantic representation shown in figure~\ref{politics}.
An indexing process that follows certain linked entities
could, for example, index the Question Time home page
against the keywords ``politics'' or index a film's
page against the names of actors that appear therein.
Linked concepts might also drive decorations and controls
on the search results pages themselves or the search
application might even be able to provide faceting, filtering
and aggregation across content that shares common properties.

\begin{sidewaysfigure}
  \begin{center}
    \begin{tikzpicture}[scale=0.6,transform shape]
    \begin{dot2tex}[dot,pgf,codeonly]
      \input{politics.dot}
    \end{dot2tex}
    \end{tikzpicture}
  \end{center}
  \caption{Semantic metadata around the \emph{Politics} programme genre}
  \label{politics}
\end{sidewaysfigure}

@@

The time and date of the next broadcast of this episode is also shown.
From the graph depicted, we can see there is a
broadcast to occur on Sunday, 11 May 2014 on the BBC Parliament
channel. Again, this is information that can be displayed within
search results that might well answer some queries directly
such as ``When is Question Time next on TV?''. This is similar
to functionality offered by Google where currency conversions,
flight times and other quick answers are displayed at the top
of the results for any query it deems has a straight answer.

Finally, note there are some metadata about the pages themselves
that are repeated within the Open Graph protocol namespace
(prefixed with \texttt{og:}). It is common for BBC pages (and
in fact pages on the web in general) to have embedded Open
Graph metadata to integrate into Facebook's social graph, even
when no other semantic markup or metadata are present. Whilst
the original intention was for Facebook integration, linked
data technologies will allow us to derive information from
these properties beyond their intended purpose.

Overall, there are a lot of metadata obtainable about BBC
programmes via semantic markup available on the public web.
However, there is
still some information that we cannot obtain:

\begin{itemize}
  \item We cannot easily gather a list of all identifiers that might
    be interesting to the search application. Crawling links with
    web crawlers is one approach, but there is no guarantee of finding
    everything and there are difficulties knowing when to get an
    updated version of a page when it changes. A BBC-specific
    search can and arguably should make use of internal integration
    to discover and update programmes information as it is created,
    changed or removed.
  \item BBC iPlayer can display the names of contributors to a programme
    such as the producers, directors, actors, etc. This information
    does not appear to be present in the semantic metadata within
    the programmes microsites.
  \item Linked Data follows an \emph{Open World} assumption,
    which means that the lack of fact being asserted does not imply
    that fact is not true. In our Question Time example above, the
    fact that Question Time is not asserted to be a comedy does not
    strictly imply that it is not a comedy.
\end{itemize}

@@

In this example, missing off the link to iPlayer might merely
inconvenience a user who has to click around a bit more to
find the iPlayer link. If, however, the search application
chose not to respond with the programme at all under the
impression it is not available to watch, then there is
arguably a more broken user experience.

@@

The trade-offs between open and closed world assumptions need to
be kept in mind for any information architecture around the
search results pages and for any domain modelling for the
search indexes. Care should be taken around any design element
or feature that is affected by the lack of information. Ideally,
all behaviour would follow a \emph{progressive enhancement} model
where additional information can only improve the system's
behaviour
and the omission of details or data leads to a \emph{degraded}
rather than \emph{broken} experience.

The programmes data set is normally the most structured and
complex to work with, but is one of the leading uses of
semantic web technologies on the BBC website as a whole. In
the rest of this section, I will briefly touch on any different
challenges from other data sets.

@@

The semantic metadata that can be found in a BBC News article
page is notably less complex than a programmes microsite, as
can be seen in figure~\ref{keepod}.

\begin{sidewaysfigure}
  \begin{center}
    \begin{tikzpicture}[scale=0.5,transform shape]
    \begin{dot2tex}[dot,pgf,codeonly]
      \input{keepod.dot}
    \end{dot2tex}
    \end{tikzpicture}
  \end{center}
  \caption{Metadata found within a BBC News article page}
  \label{keepod}
\end{sidewaysfigure}

As discussed in section~\ref{programmes}, BBC News also makes
use of Facebook's Open Graph metadata and a search application
could derive information about this article from those properties.

@@

\begin{sidewaysfigure}
  \begin{center}
    \begin{tikzpicture}[scale=0.41,transform shape]
    \begin{dot2tex}[dot,pgf,codeonly]
      \input{keepod-tagged.dot}
    \end{dot2tex}
    \end{tikzpicture}
  \end{center}
  \caption{BBC News article page's metadata enriched using DBPedia Spotlight}
  \label{keepod-tagged}
\end{sidewaysfigure}

@@

One remaining piece of information that is still lacking is
the News category in which the article falls. The BBC News
website has business rules around categorising all news
content -- e.g. \emph{Technology}, \emph{Scotland}, \emph{Education}
-- but this categorisation seems lacking from the semantic markup. The
current BBC Search application decorates all news results with
their respective news category, so an indexing chain using
the linked data within the news pages alone would need need
to enrich with that information.

@@

The BBC Sport website shares a lot with BBC News in that a large
amount of the content is article-based. However, the sport domain
has a lot of structured data beneath the surface: atheletes,
teams, competitions, disciplines, events, etc.

An ontology was defined to drive some automatically aggregated
pages during the 2012 Olympics\cite{rayfield2011bbc}, but reading
semantic data from a typical article yields a picture very similar
to the News story example in figure~\ref{keepod}.

There is a lot of potential for structured data to create an
intelligent search experience whereby, for example, searching
for a football team by name would suggest links to the last
match results, dates of when they are next playing or even
summarise the current league table for the relevant football
league. This is something for much later than the proposed
road map in this paper, but it can be hoped that improvements
from using linked data in other areas of the BBC can inspire
some interesting collaboration with the BBC Sport teams.

\subsection{Knowledge and Learning}

The ``Knowledge and Learning'' brand is an attempt to create
a consistent and cohesive picture of what was a discrete
collection of sites. Topics search as school curricula, revision
guides, science, religion, food and history have structured
domain models behind them, but there are limited semantic data
within the pages themselves. This means the best option for
the current search application is to run a web crawler across
these sites, but there are some efforts to create relevant
ontologies to drive these sites.

One example is the the \emph{Education} website that has
a distinct page for every school stage, school subject
and topic within a subject for all the the UK. These pages
are driven off a domain model and ontology\cite{bbc2013curriculum}
behind the scenes
(i.e. it's not present within the HTML pages), but that
model has been published under a free licence.
\cite{bbc2014curriculum} This freely-available data set
effectively acts as site map of the Education website.

\subsection{Legacy Sites}

With websites that are no longer maintained, there is little choice
but to run web crawlers over these pages. Further complication
comes from the fact that certain pages may be taken down
altogether without the search application necessarily being
notified, so the crawler has to periodically check on
pages already indexed to confirm they are still there.

### 2014-05-20 chapter3.2.tex
Sort of finished chapter 5!
Done! Reviewed and ready to submit.

\section{Search Results Page}

The majority of the complexity and development arguably lies within
the indexing processes of the search applicatio, but it is with the
\emph{actual Search Engine Results Page} (SERP) that the website users interact.

@@

The different categories/zones are shown on the left menu, with the
number of results found within each category also shown. The first results
are ``Editor's Choice'' results where the application
has matched manually-curated pages against the query. This module appears
as its own distinct category at the top of the list, but functionally
is a distinct feature to the ``organic'' results that follow below.

The organic results are broken into categories such that this ``All Results''
page reached after a search acts as a way to skim over each relevant
category.

@@

There is a feature of the current search application where data or metadata
are more directly published and that is the ``Editor's Choice'' feature. In
the next section, the nature of that metadata is explored further.

>>>>

\section{Search Results Page}
\label{sec:search-results-page}

The majority of the complexity and development arguably lies within
the indexing processes of the search application, but it is with the actual
\emph{Search Engine Results Page} (SERP) with which the website users interact.

@@

In figure~\ref{fig:search-page},
the different categories/zones are shown on the left menu, with the
number of results found within each category also shown. The first results
are ``Editor's Choice'' results where the application
has matched manually-curated pages against the query. This module appears
as its own distinct category at the top of the list, but functionally
is a distinct feature to the ``organic'' results that follow below.

@@

There is also a feature of the current search application where data or metadata
are more directly published and that is the ``Editor's Choice'' feature. In
the next section, the nature of that metadata is explored further.

### 2014-05-20 chapter3.3.tex
Done! Reviewed and ready to submit.

Three different categories of search activities were proposed
as part of a model developed by
Gary Marchionini\cite{marchionini2006exploratory}:
\emph{Lookup}, \emph{Learn} and \emph{Investigate}. The
latter two can be grouped under the banner of \emph{exploratory search}
and the diverse spread of organic results on the search results pages
can aid these activities. It is to serve the \emph{Lookup} activity
that the so-called organic results are header with up to three
``Editor's Choice'' links that -- based on the query given -- may
well lead directly to a specific item or location the user was seeking.

Two such distinct modules on the page allow both lookup- and exploration-
style interactions to occur on the same results page. It could be said
that the Google Knowledge Graph\cite{singhal2012introducing} takes
this concept further to provide summaries of entities and links to
specific answers alongside the traditional, keyword-based matches.

The Editor's Choice feature assures that common -- or easily recognisable -- queries
lead to a mix of mechanically-chosen and editorially-curated links,
with the intention this provides a balance between the large-scale
matching of a search engine with some human insight into content
most users are likely to be looking for -- intelligence that is not
so easily bestowed upon a search engine.

Howver, each and every link promoted within this feature is hand-chosen by editorial
staff and much manual effort is needed to keep promoting new concepts
as they appear and to remove pages as they get superseded.

>>>>

Three different categories of search activities were proposed
as part of a model developed by
Gary Marchionini\cite{marchionini2006exploratory}:
\emph{Lookup}, \emph{Learn} and \emph{Investigate}. The
latter two can be grouped under the banner of \emph{exploratory search}
and the diverse spread of organic results on the search results pages
can aid these activities. It is to serve the \emph{Lookup} activity
that the so-called organic results are headed with up to three
``Editor's Choice'' links that -- based on the query given -- may
well lead directly to a specific item or location the user was seeking.

Having both the organic results and the Editor's Choice links
allow both lookup- and exploration-
style interactions to occur on the same results page. It could be said
that the Google Knowledge Graph\cite{singhal2012introducing} takes
this concept further to provide summaries of entities and links to
specific answers alongside the traditional, keyword-based matches.

The Editor's Choice feature assures that common -- or easily recognisable -- queries
lead editorially-curated links in addition to algorithmically-chosen pages,
with the intention this provides a balance between the large-scale
matching of a search engine with some human insight into content
most users are likely to be looking for -- intelligence that is not
so easily bestowed upon a search engine.

However, each and every link promoted within this feature is hand-chosen by editorial
staff and much manual effort is needed to keep promoting new concepts
as they appear and to remove pages as they get superseded.
